Learning and comparing functional connectomes across subjects

### 2013-01-01 paper.tex
start intro

Horwitz \emph{el al.}\ \cite{horwitz1995} mentioned almost 20 years ago
that ``the crucial concept needed for network analysis is covariance''.

>>>>

Horwitz \emph{el al.}\ \cite{horwitz1995} claimed almost 20 years ago
that ``the crucial concept needed for network analysis is covariance''.
In our eyes, this still holds today. Estimation of noiseless functional
connectomes relies largely on fitting covariance models.
